draft

### 2025-05-18 draft.tex
docs: Update feature section titles

% Created 2025-05-17 Sat 20:18
% Intended LaTeX compiler: pdflatex
\documentclass{article}

@@

The core target users of such a tool would be biologists and data scientists who need reproducibility and data within a few lines of code. As a whole, there is still a role to be played for engineered features to, at the very least, complement deep learning ones. The community is missing a generalist tool that converts images and masks into representative vectors without the need of interfaces or cloud compute and that integrates seamlessly with other scientific libraries. This is the role that we envision cp\_measure can occupy in the scientific software ecosystem.
\section{Extraction of interpretable features using cp\_measure}
\label{sec:org5633614}
In cp\_measure, we isolated the CellProfiler measurements and categorize them based on their inputs: One object and one imaging channel (e.g., intensity, texture), one object and multiple channels (such as correlation features) and multiple objects (e.g., number of neighbors).

>>>>

% Created 2025-05-17 Sat 20:28
% Intended LaTeX compiler: pdflatex
\documentclass{article}

@@

The core target users of such a tool would be biologists and data scientists who need reproducibility and data within a few lines of code. As a whole, there is still a role to be played for engineered features to, at the very least, complement deep learning ones. The community is missing a generalist tool that converts images and masks into representative vectors without the need of interfaces or cloud compute and that integrates seamlessly with other scientific libraries. This is the role that we envision cp\_measure can occupy in the scientific software ecosystem.
\section{Extracting interpretable features}
\label{sec:org61842b5}
In cp\_measure, we isolated the CellProfiler measurements and categorize them based on their inputs: One object and one imaging channel (e.g., intensity, texture), one object and multiple channels (such as correlation features) and multiple objects (e.g., number of neighbors).
